Functory: Distributed Computing for the Common Man\thanks{This research was partly supported by the French national project U3CAT (\emph{Unification of Critical C Code Analysis Techniques}, ANR-08-SEGI-021).}

### 2010-10-06 doc/report/main.tex
*** empty log message ***

The first example is the classical $N$-queens problem, where we
compute the total number of ways to place $N$ queens on a $N\times N$
chessboard in such a way no two queens attack each other.
We use a standard backtracking algorithm for this problem, which
places the queens one by one starting from the first row.
Distributing the computation is thus quite easy: we consider all
possible ways to place queens on the first $D$ rows and then perform
the subsequent search in parallel. Choosing $D=1$ will result in
exactly $N$ tasks. More subtly, $D=2$ will result in $N^2-3N+2$ tasks.
% TODO: make a picture to illustrate positioning of 2 queens on the
% first 2 rows

Each tasks only consists of three integers and results in one integer,
which is the total number of solutions for this task.
We make use of function \of{map_local_fold} from the derived API,
where \of{map} is performing the search and \of{fold} simply adds the
intermediate results.

@@

@@

>>>>

The first example is the classical $N$-queens problem, where we
compute the total number of ways to place $N$ queens on a $N\times N$
chessboard in such a way no two queens attack each other.
We use a standard backtracking algorithm for this problem, which
places the queens one by one starting from the first row.
Distributing the computation is thus quite easy: we consider all
possible ways to place queens on the first $D$ rows and then perform
the subsequent search in parallel. Choosing $D=1$ will result in
exactly $N$ tasks; choosing $D=2$ will result in $N^2-3N+2$ tasks; and
so on.
% TODO: make a picture to illustrate positioning of 2 queens on the
% first 2 rows

Each task only consists of three integers and its result is one integer,
which is the total number of solutions for this task.
We make use of function \of{map_local_fold} from the derived API,
where \of{map} is performing the search and \of{fold} simply adds the
intermediate results.

@@

Drawing the Mandelbrot set is another classical example that could be
distributed easily, since the color of each point can be computed
independently of the others. 
Let us assume we are given the coordinates of the region to be drawn,
along with the width \of{w} and height \of{h} of the resulting image
(in pixels). 
Let us assume the total number of tasks $\of{t} \ge 1$ is given as a
parameter. It is immediate to split the image into \of{t} sub-images,
each of which is computed in parallel with and independently of the
others. For instance, the image could be split into horizontal slices
or, more generally, into rectangular blocks.

Each task is thus four floating-point numbers denoting the region
coordinates, together with two integers denoting the dimensions of the
sub-image to be drawn. The result of the task is a matrix of pixels,
of size $(\of{w}\times\of{h}) / \of{t}$. 
For instance, drawing a $800\times 600$ image using 20 tasks will
result in 20 sub-images of size $176,000$ bytes each,
assuming each pixel is encoded in four bytes.

@@

\subsubsection{Matrix Multiplication}

$\of{n} = \of{p} = \of{m} = 100$

coefficients have several thousands of digits; we use GMP

%            parall  line

% # tasks    10,000   100

% sequential  20.3   20.2
% cores 2     22.7   11.3
% cores 4     12.3    6.1
% cores 6      8.6    4.3
% cores 8      8.0    3.5

% network is localhost(moloch) + belzebuth

% network 3+3        12.7
% network 6+  112     7.2
% network  +6   ?    36.4
% network 6+6  76.1  11.9

\begin{center}
  \begin{tabular}{|l|l|l|}
    \hline
    sequential & cores & network \\\hline
    20.3 & 
  \end{tabular}
\end{center}
